---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


##Loading and preprocessing the data
```{r}
    data <- read.csv("activity.csv")
    data0 <- data
    data <- data[complete.cases(data), ]
```


##The mean total number of steps taken per day
```{r}
    days <- 0:60
    total <- c()
    for (i in days) {
        d <- as.Date("2012-10-01") + i
        d <- as.character(d)
        cond <- as.character(data$date) == d
        x <- data[cond, ]
        if (!nrow(x) == 0) {
            total <- c(total, sum(x$steps) * 1.0)
        }
    }
    mean1 <- mean(total)
    median1 <- median(total)

    hist(total)
```
```{r, echo=FALSE}
    cat("The mean total number of steps taken per day is")
    print(mean1)
    cat("The median total number of steps taken per day is")
    print(median1)
```
##The average daily activity pattern
```{r}
library(ggplot2)

    n <- 24 * 60 / 5 -1
    x <- 0:n
    for (i in days) {
        d <- as.Date("2012-10-01") + i
        d <- as.character(d)
        cond <- as.character(data0$date) == d
        xxx <- data0$steps[cond]
        if (d == "2012-10-01")  {
            yyy <- xxx
        }
        else  {
            yyy <- cbind(yyy, xxx)
        }
    }
    step <- sapply(yyy, mean, na.rm=TRUE)
    x <- x * 5
    df <- data.frame(interval=x, Steps=step)
    p <- ggplot(data=df, aes(x=interval, y=Steps))
    p <- p + geom_line()
```
Graph of average steps in intervals
```{r}
    print(p)
    m <- max(step, na.rm=TRUE)
    cond <- df$Steps == m
    mm <- df$interval[cond]
    mm <-mm[!is.na(mm)]
```
interval at wich maximum average steps are taken
```{r, echo=FALSE}
    print(mm)
```

##Imputing missing values
```{r}
    nna <- 0
    for (i in days)  {
        d <- as.Date("2012-10-01") + i
        d <- as.character(d)
        cond <- as.character(data0$date) == d
        xxx <- data0$steps[cond]
        cond <- is.na(xxx)
        zzz <- xxx[cond]
        nna <- nna + length(zzz)
    }
```
Total number of missing values is
```{r, echo=FALSE}
    print(nna)
```
```{r}
    n <- 24 * 60 / 5
    x <- 1:n
    step1 <- c()
    sub <- mean1 / 24 / 12.0 
    for (i in days)  {
        d <- as.Date("2012-10-01") + i
        d <- as.character(d)
        cond <- as.character(data0$date) == d
        xxx <- data0$steps[cond]
        for (j in x)  {
            if (is.na(xxx[j]))  {
                xxx[j] <- sub 
            }
        }
        step1 <- c(step1, xxx)
    }
    date <- data0$date
    interval <- data0$interval
    data1 <- data.frame(date=date, steps=step1, interval=interval)
    total1 <- c()
    for (i in days)  {
        d <- as.Date("2012-10-01") + i
        d <- as.character(d)
        cond <- as.character(data1$date) == d
        xxx <- data1$steps[cond]
        total1 <- c(total1, sum(xxx))
    }
    hist(total)
    mean2 <- mean(total1)
    median2 <- median(total1)
```
```{r, echo=FALSE}
    print("")
```
Mean of total steps per day with missing value filled
```{r, echo=FALSE}
    print(mean2)
```
Median of total steps per day with missing value filled
```{r, echo=FALSE}
    print(median2)
```

## Are there differences in activity patterns between weekdays and weekends?
```{r}
    data1$day <- weekdays(as.Date(as.character(data1$date)))
    cond <- data1$day == "土曜日" | data1$day == "日曜日"
    xxx <- data1$steps[cond]
    yyy <- data1$steps[!cond]
    t.test(xxx, yyy)    
```
Activity is significantly higher in weekdays than weekends.